### 2016-02-18 paper/4-performance.tex
Changed the SCS style to make captions 9pt instead of 8pt; slight modifications to keep everything on 8 pages; removed keyword C++11

\newcommand{\plotfraction}{0.9}

@@

    \item The \textit{HighInterconnect} model, a merge of PHOLD~\cite{PHOLD} and the \textit{HI} model of DEVStone~\cite{DEVStone}, creates $n$ atomic models, where each model has exactly one output port.
          Similar to PHOLD, all models are connected to one another, but all through the same port: every model receives each generated event.
          The model takes one parameter: the number of models.
          This benchmark investigates the complexity of event routing, and how the simulation kernel handles many simultaneous events.
          An example for four models is shown in Figure~\ref{fig:interconnect_model}.
\end{enumerate}

@@

    \includegraphics[width=\modelfraction\columnwidth]{fig/interconnect_model.pdf}
    \caption{HighInterconnect model for three models.}
    \label{fig:interconnect_model}

@@

Only the Queue and HighInterconnect models are relevant for sequential simulation, so we do not use the PHold model yet.

@@

\subsubsection{HighInterconnect}
In the HighInterconnect model, we increase the number of atomic models, thus quadratically increasing the number of couplings and the number of external transitions.
As can be seen in Figure~\ref{fig:Interconnect_benchmark}, adevs outperforms dxex by a fair margin.
Analysis showed that this is caused by the high amount of exchanged events: event creation is much slower in dxex than it is in adevs, despite dxex's use of memory pools.

>>>>

\newcommand{\plotfraction}{0.85}

@@

    \item The \textit{Interconnect} model, a merge of PHOLD~\cite{PHOLD} and the \textit{HI} model of DEVStone~\cite{DEVStone}, creates $n$ atomic models, where each model has exactly one output port.
          Similar to PHOLD, all models are connected to one another, but all through the same port: every model receives each generated event.
          The model takes one parameter: the number of models.
          This benchmark investigates the complexity of event routing, and how the simulation kernel handles many simultaneous events.
          An example for four models is shown in Figure~\ref{fig:interconnect_model}.
\end{enumerate}

@@

    \vspace{0.2cm}

    \includegraphics[width=\modelfraction\columnwidth]{fig/interconnect_model.pdf}
    \caption{Interconnect model for three models.}
    \label{fig:interconnect_model}

    \vspace{0.2cm}

@@

Only the Queue and Interconnect models are relevant for sequential simulation, so we do not use the PHold model yet.

@@

\subsubsection{Interconnect}
In the Interconnect model, we increase the number of atomic models, thus quadratically increasing the number of couplings and the number of external transitions.
As can be seen in Figure~\ref{fig:Interconnect_benchmark}, adevs outperforms dxex by a fair margin.
Analysis showed that this is caused by the high amount of exchanged events: event creation is much slower in dxex than it is in adevs, despite dxex's use of memory pools.
